### 2024-06-27 bugs.qmd
20240627 - sessionInfo() for reproducibility

- `players` database has a season column but it is only populated for some players, and it is only populated with 2020
- `player_stats` database of weekly stats does not have a `game_id` column

>>>>

- `players` database has a season column but it is only populated for some players, and it is only populated with 2020 (<https://github.com/nflverse/nflreadr/issues/238>)
- `player_stats` database of weekly stats does not have a `game_id` column (<https://github.com/nflverse/nflreadr/issues/238>)

<https://github.com/nflverse/nflreadr/issues/237>

### 2024-06-27 getting-started.qmd
20240627 - sessionInfo() for reproducibility

>>>>

::: {.content-visible when-format="html"}

## Session Info {#sec-gettingStartedSessionInfo}

At the end of each chapter in which `R` code is used, I provide the session information, which describes the system and operating system the code was run on and the versions of each package.
That way, if you get different results from me, you can see which differ, to help with reproducibility.
If you run the (all of) the exact same code as is provided in the text, in the exact same order, with the exact same setup (platform, operating system, package versions, etc.), you should get the exact same answer as is in the text.
That is the idea of reproducibility—getting the exact same result with the exact same inputs.
Reproducibility is crucial for studies to achieve greater confidence in their findings and to ensure better replicability of findings across studies.

```{r}
sessionInfo
```

:::
